---
title: "simulation"
author: "gyu"
date: '2020 3 27 '
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
set.seed(2016)
```

## Simulations

In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.

Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponentials.
```{r cars}
lambda<- 0.2
sample_size <- 40
simulations <- 1000
sim_matrix <- matrix(rexp(simulations*sample_size, rate=lambda), simulations, sample_size)
sim_mean <-rowMeans(sim_matrix)
hist(sim_mean,xlab= "The 40 exponentials mean", ylab="Frequency",main= "Histogram of mean of 40 exponentials")  
```

## Show the sample mean and compare it to the theoretical mean of the distribution.
```{r}
sample_mean <- mean(sim_mean)
theoretical_mean <- 1/lambda
```

## Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
```{r}
sampleVar <- var(sim_mean)
theoVar  <- (1 / lambda)^2 /sample_size 
sampleSD <- sd(sim_mean)
theoSD <- 1/(lambda * sqrt(sample_size))
```

## Show that the distribution is approximately normal.

```{r pressure, echo=FALSE}
plotdata <- data.frame(sim_mean)
m <- ggplot(plotdata, aes(x =sim_mean))
m <- m + geom_histogram(aes(y=..density..), colour="black",
                        fill = "lightblue")
m <- m + labs(title = "Distribution of averages of 40 Samples", x = "Mean of 40 Samples", y = "Density")
m <- m + geom_vline(aes(xintercept = sample_mean, colour = "green"))
m <- m + geom_vline(aes(xintercept = theoretical_mean, colour = "violet"))
m <- m + stat_function(fun = dnorm, args = list(mean = sample_mean, sd = sampleSD), color = "blue", size = 1.0)
m <- m + stat_function(fun = dnorm, args = list(mean = theoretical_mean, sd = theoSD), colour = "red", size = 1.0)
m
```

The theoretical mean and the sample mean are so close that they overlap.
the distribution of averages of 40 exponential distributions is close to the normal distribution with the expected theoretical values based on the given lambda.
```{r pressure, echo=FALSE}
sampleConfInterval <- round (mean(sim_mean) + c(-1,1)*1.96*sd(sim_mean)/sqrt(sample_size),3)
```


```{r pressure, echo=FALSE}
theoConfInterval <- theoretical_mean + c(-1,1) * 1.96 * sqrt(theoVar)/sqrt(sample_size)
theoConfInterval

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
