---
title: "course_project"
author: "gyu"
date: '2020 3 31 '
output:
  pdf_document: latex-engine: xelatex
---
# course project
They are particularly interested in the following two questions

- Is an automatic or manual transmission better for MPG?
- Quantify the MPG difference between automatic and manual transmissions

## data loading
Loading data set of a collection of cars
```{r}
library(ggplot2)
library(tinytex)
data(mtcars)
```

## data description
```{r}
str(mtcars)
```

## data transformation
change data types, and labeling transmission type.
```{r}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am <- factor(mtcars$am,labels=c('Automatic','Manual'))
```

# compare transmission
compare transmission type by boxplot
```{r}
boxplot(mpg ~ am, data=mtcars, col=(c("red","lightblue")), xlab="Transmission", ylab="mpg", main="compare Automatic vs Manual")
```
compare average
```{r}
tapply(mtcars$mpg,mtcars$am,mean)
```
perform t test (h0 : Automatic = Manual)
```{r}
t.test(mpg ~ am, data = mtcars)
```
we can reject h0

test by regression
```{r}
trans_lm = lm(mpg~am,data=mtcars)
summary(trans_lm)
```
p-value is less than 0.001, so we can reject


## regression analysis
select model by forward and backward selection
```{r}
base_fit <- lm(mpg ~ ., data = mtcars)
fit1 = step(base_fit,direction = "both")
```

```{r}
summary(fit1)
```
adjusted r square value is 0.84
use anova to compare with base model
```{r}
anova(fit1,base_fit)
```
p-value is very high. so variables not in model1 is not necessary

see model residuals
```{r}
par(mfrow = c(2, 2))
plot(fit1)
```
## conclusion

- Cars with Manual get more mpg compared aganist cars with Automatic. 
- mpg will decrease by factor of cyl, hp, wt and amMaual